Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-20 lloveras_2020.tex
agregado de texto de nishtha

% Definitions for the journal names
\newcommand{\adv}{    {\it Adv. Space Res.}} 
\newcommand{\annG}{   {\it Ann. Geophys.}} 
\newcommand{\aap}{    {\it Astron. Astrophys.}}
\newcommand{\aaps}{   {\it Astron. Astrophys. Suppl.}}
\newcommand{\aapr}{   {\it Astron. Astrophys. Rev.}}
\newcommand{\ag}{     {\it Ann. Geophys.}}
\newcommand{\aj}{     {\it Astron. J.}} 
\newcommand{\apj}{    {\it Astrophys. J.}}
\newcommand{\apjs}{   {\it Astrophys. J. Suppl.}}
\newcommand{\apjl}{   {\it Astrophys. J. Lett.}}
\newcommand{\apss}{   {\it Astrophys. Space Sci.}} 
\newcommand{\cjaa}{   {\it Chin. J. Astron. Astrophys.}} 
\newcommand{\gafd}{   {\it Geophys. Astrophys. Fluid Dyn.}}
\newcommand{\grl}{    {\it Geophys. Res. Lett.}}
\newcommand{\ijga}{   {\it Int. J. Geomagn. Aeron.}}
\newcommand{\jastp}{  {\it J. Atmos. Solar-Terr. Phys.}} 
\newcommand{\jgr}{    {\it J. Geophys. Res.}}
\newcommand{\mnras}{  {\it Mon. Not. Roy. Astron. Soc.}}
\newcommand{\nat}{    {\it Nature}}
\newcommand{\pasp}{   {\it Pub. Astron. Soc. Pac.}}
\newcommand{\pasj}{   {\it Pub. Astron. Soc. Japan}}
\newcommand{\pre}{    {\it Phys. Rev. E}}
\newcommand{\solphys}{{\it Solar Phys.}}
\newcommand{\sovast}{ {\it Soviet  Astron.}} 
\newcommand{\ssr}{    {\it Space Sci. Rev.}}

@@

\diego{
A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. In previous work, DEMT has been combined with a potential field source surface (PFSS) model such as \citet{huang_2012}, \citet{nuevo_2013} and \citet{nuevo_2015}. Recently, \citet{lloveras_2017} combined DEMT whit PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines.}

\diego{The Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework model is constantly validated with observations as new improvements are implemented, in particular, \citet{oran_2015} used DEMT to validate the model in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT resutls in a globally fashion, obtaining an agreement within 20\%.
We used AWSoM results with two purposes. On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
}\\
We carry out a quantitatively detailed comparative \diego{DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24. To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} (EUVI-B) on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used \diego{for DEMT, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM}, while data taken by the \textit{Atmospheric Imaging Assembly instrument} (AIA), on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208 \diego{for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.

@@

@@

\notebyalbert{Chip: In relation to the previous comment, if the analysis proposed in Figure 15 is carried out we should say something about that here.}

A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is currently only possible with tomographic techniques, such as DEMT. Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models. In {follow up articles} we will {carry out the 3D DEMT reconstruction and MHD modeling of} new target rotations {selected from} the current solar minimum {epoch} between SCs 24 and 25, {as well as rotation CR-2219 corresponding to the July 2nd 2019 total solar eclipse.}
\begin{acks}
D.G.Ll. and C.M.C. {acknowledge} CONICET doctoral {fellowships} (Res. Nr. 4870) to IAFE that supported {their} participation in this research. {D.G.Ll, A.M.V., F.A.N. and C.M.C. acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research. A.M.V. also acknowledges UBACyT grant 20020160100072BA to DCAO-UBA to FCEyN-UBA and IAFE that partially supported his participation in this research.}
\end{acks}
\\
\\
\begin{footnotesize}
 Disclosure of Potential Conflicts of Interest: The authors declare that they have no conflicts of interest.
\end{footnotesize}
\bibliographystyle{spr-mp-sola}
\bibliography{solphys_dglloveras}

>>>>

% Definitions for the journal names
\newcommand{\adv}{    {\it Adv. Space Res.}} 
\newcommand{\annG}{   {\it Ann. Geophys.}} 
\newcommand{\aap}{    {\it Astron. Astrophys.}}
\newcommand{\aaps}{   {\it Astron. Astrophys. Suppl.}}
\newcommand{\aapr}{   {\it Astron. Astrophys. Rev.}}
\newcommand{\ag}{     {\it Ann. Geophys.}}
\newcommand{\aj}{     {\it Astron. J.}} 
\newcommand{\apj}{    {\it Astrophys. J.}}
\newcommand{\apjs}{   {\it Astrophys. J. Suppl.}}
\newcommand{\apjl}{   {\it Astrophys. J. Lett.}}
\newcommand{\apss}{   {\it Astrophys. Space Sci.}} 
\newcommand{\cjaa}{   {\it Chin. J. Astron. Astrophys.}} 
\newcommand{\gafd}{   {\it Geophys. Astrophys. Fluid Dyn.}}
\newcommand{\grl}{    {\it Geophys. Res. Lett.}}
\newcommand{\ijga}{   {\it Int. J. Geomagn. Aeron.}}
\newcommand{\jastp}{  {\it J. Atmos. Solar-Terr. Phys.}} 
\newcommand{\jgr}{    {\it J. Geophys. Res.}}
\newcommand{\mnras}{  {\it Mon. Not. Roy. Astron. Soc.}}
\newcommand{\nat}{    {\it Nature}}
\newcommand{\pasp}{   {\it Pub. Astron. Soc. Pac.}}
\newcommand{\pasj}{   {\it Pub. Astron. Soc. Japan}}
\newcommand{\pre}{    {\it Phys. Rev. E}}
\newcommand{\solphys}{{\it Solar Phys.}}
\newcommand{\sovast}{ {\it Soviet  Astron.}} 
\newcommand{\ssr}{    {\it Space Sci. Rev.}} 
\newcommand{\procspie}{{\it Proc. SPIE}}

@@

\diego{
A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. In previous works, DEMT has been combined with a potential field source surface (PFSS) model such as \citet{huang_2012}, \citet{nuevo_2013} and \citet{nuevo_2015}. Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines.}

\diego{The Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework model is constantly validated with observations as new improvements are implemented, in particular, \citet{oran_2015} used DEMT to validate the model in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT resutls in a globally fashion, obtaining an agreement within 20\%.
We used AWSoM results with two purposes. On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
}\\
We carry out a quantitatively detailed comparative \diego{DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24. To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} \diego{(EUVI-B \citep{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used \diego{for DEMT, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM}, while data taken by the \textit{Atmospheric Imaging Assembly instrument} \diego{(AIA \citep{lemen_2012})}, on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208 \diego{for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.

@@

The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014}. AWSoM addresses coronal heating by including the non-linear interaction of forward propagating and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature. The dissipated turbulent energy is distributed over these three temperatures based on the theories of linear wave damping and stochastic heating. AWSoM does not use ad-hoc heating functions and accounts for both collisional and collision-less electron heat conduction. The Alfv\'{e}n wave number associated with the damping rate is determined by the critical balance condition which uses the cascade time of the minor wave \citep{Lit2007} instead of the previously used cascade time of the major wave \citep{Cha2011, Van2014}. This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration \diego{falta cita}%\citep{Van2019b}.
To solve anisotropic MHD equations with radiative cooling, heat conduction and wave turbulence, AWSoM uses the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme. MHD equations employed within the AWSoM model are detailed in \citet{Van2014}. Recently, \citet{sachdeva_2019} validated the AWSoM simulation results with a suite of observations from near the Sun upto 1 AU for solar minimum conditions.

Global maps of the observed photospheric magnetic field are essential for accurate modeling of the solar corona and are the primary input for AWSoM. We use the Global Oscillation Network Group (GONG) synoptic map as input for CR2082 (2009-04-05 - 2009-05-03) and the Air Force Data Assimilation Photospheric Flux Transport (ADAPT)-GONG global magnetic field map for CR2208 (2018-09-02 to 2018-09-29). ADAPT-GONG maps are unavailable for CR2082. GONG provides synoptic full disk line-of-sight surface map of the radial magnetic field component. The unobserved polar fields in GONG are estimated by fitting a polynomial to neighboring observed fields. An improvement over these maps is provided by the ADAPT model \citep{Wor2000} which creates synchronic-synoptic maps that uses supergranulation, meridional circulation, flux-transport and differential rotation to evolve the magnetic field on the Sun for better estimates of the unobserved photospheric field \citep{Arg2010, Hen2012}. 
In AWSoM, the 2D radial photospheric field is converted to 3D magnetic field using the Potential Field Source Surface (PFSS) model which specifies the initial condition. We take the source surface to be at 2.5 \rsun and the magnetic field is radial at this height. The radial component specifies the boundary condition.
%ADAPT-GONG maps have multiple realizations based on how the polar fields are filled. We use realization 5 for CR2208.
 Based on \citet{Cha2011} the stochastic heating exponent is taken to be 0.21 and amplitude is 0.18 to account for energy partioning between electrons and protons. The Alfv\'{e}n wave energy boundary condition is given by the poynting flux (S$_{A}$) of the outgoing wave $(\frac{S_{A}}{B})_{\odot} = 1.0\times 10^{6}$ Wm$^{-2}$T$^{-1}$ and the correlation length of the Alfv\'{e}n waves is set to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$ m$\sqrt{T}$.

The base of the transition region forms the inner boundary of the model (at $\approx$1.0\,\rsun). To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot}=2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K. The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}. In reality, the thin transition has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses. To resolve these gradients excessive numerical resources are required. As described in \citet{Lio2009,Sok2013} we artificially broaden the transition region to resolve with our finest grid resolution of $\approx$ 0.001\,\rsun.This results in pushing the corona outwards. At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region.
The computational domain for solar corona (SC) extends from 1 to 24 R$_{\odot}$. The spherical grid in SC is radially stretched (with a maximum resolution of 0.001 R$_{\odot}$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh Refinement (AMR) resolves the angular size to 1.4$^\circ$ between 1 - 1.7 \rsun and 2.8 \rsun outside. The SC component uses about 3 million cells on a $6 \times 8 \times 8$ grid block. Local time stepping is used to speed up the steady state convergence. AWSoM simulation results provide the 3D distribution of density and temperature in addition to the 3D magnetic structure and velocity of the solar wind.

@@

\notebyalbert{Chip: In relation to the previous comment, if the analysis proposed in Figure 15 is carried out we should say something about that here.} d

A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is currently only possible with tomographic techniques, such as DEMT. Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models. In {follow up articles} we will {carry out the 3D DEMT reconstruction and MHD modeling of} new target rotations {selected from} the current solar minimum {epoch} between SCs 24 and 25, {as well as rotation CR-2219 corresponding to the July 2nd 2019 total solar eclipse.}

\begin{acks}
D.G.Ll. and C.M.C. {acknowledge} CONICET doctoral {fellowships} (Res. Nr. 4870) to IAFE that supported {their} participation in this research. {D.G.Ll, A.M.V., F.A.N. and C.M.C. acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research. A.M.V. also acknowledges UBACyT grant 20020160100072BA to DCAO-UBA to FCEyN-UBA and IAFE that partially supported his participation in this research.}
\end{acks}
\\
\\
\begin{footnotesize}
 Disclosure of Potential Conflicts of Interest: The authors declare that they have no conflicts of interest.
\end{footnotesize}
\bibliographystyle{spr-mp-sola}
\bibliography{solphys_dglloveras}
